# Leaf {#cha:leaf}


```{r setup_leaf, message=FALSE, echo=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(
    cache = FALSE, echo = FALSE, 
    out.width = '80%', fig.asp = 1.2,
    warning = FALSE, fig.align = 'center',
    message = FALSE) 
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(xml2)
library(DiagrammeR)
source('_utility.R')
report <- read_csv('simulation/simulation.db.Report.csv')

df <- report %>% 
    filter(grepl('15TraitMod', Name),
           Management == 'IHN',
           Cultivar == 'hartog')

pmf <- read_xml('simulation/simulation.apsimx')


x_var <- c(
    'Wheat.Phenology.Stage',
    'Wheat.Phenology.AccumulateThermalTime')
x_lab <- 'Accumulated thermal time, stage'
```



Leaf cohort model is used in the APSIM-Wheat.

## Life growth cycle

The growth cycle of leaf cohort is divided into 7 stages and 6 periods from `Initialized` to `Detached`. The length of each period depends on the `plastrochron` and `phylochron` for initialization and appearance and is configured by `CohortParameters` for others.

Several status variables are defined for each leaf cohort, which can be used in other modules to describe the current status of leaf cohort, i.e. `IsNotAppeared`, `IsGrowing`, `IsAlive`, `IsGreen`, `IsNotSenescing`, `Senescing`, `isFullyExpanded`, `ShouldBeDead`, `IsAppeared` and `IsInitialised`. 

<div class="fig-input">
```{r leaf-life-cycle, out.width='95%', fig.asp=0.7, fig.cap='The life cycle of a leaf cohort.'}

DiagrammeR("sequenceDiagram;
	Initialized->>Appeared: Appearance 
	Appeared->>Expanded: GrowthDuration
	Expanded->>Senescing: LagDuration
	Senescing->>Senesced: SenescenceDuration
	Senesced->>Detaching: DetachmentLagDuration
	Detaching->>Detached: DetachmentDuration
    Initialized->Appeared: IsNotAppeared
    Initialized->Expanded: IsGrowing
	Initialized->>Senesced: IsAlive
	Initialized->>Senesced: IsGreen
	Initialized->>Senescing: IsNotSenescing
	Senescing->>Senesced: IsSenescing
	Expanded->>Detached: IsFullyExpanded
	Senesced->>Detached: ShouldBeDead
	Senesced->>Detached: Finished
	Appeared->>Detached: IsAppeared
	Initialized->>Detached: IsInitialised
")
```
</div>



### leaf age

The age of leaf cohort is defined as the thermal time after appearance, (i.e. keep zero after initialization). As the default values of `DetachmentLagDuration` and `DetachmentDuration` are set as `1000000` <sup>o</sup>Cd, the cohort age keeps increasing until stage `ReadyForHarvesting`.

<div class="fig-output">
```{r leaf-age, fig.cap='Age of leaf cohort as a function of stage or accumulated thermal time'}
y_cols <- c(
    'Wheat.Leaf.CohortAge')
plot_report_vector(
    df, x_var, y_cols, x_lab = x_lab, 
    y_lab = 'Age of leaf cohort (oCd)')

```
</div>


### Leaf initialization

A new leaf is initialized when the primordia number is increased by 1 at the main stem. Consequently, the total leaf cohort number is equal to total primordia number. The initialized rate of leaf cohort is equal to plastrochron.

<div class="fig-output">

```{r leaf-init-number, fig.cap='The primordia number in the main stem and initialised cohort number'}
y_cols <- c('Wheat.Structure.MainStemPrimordiaNo',
            'Wheat.Leaf.InitialisedCohortNo')

plot_report(df, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Number')

```
</div>



```{block, type='rmdimportant', echo=TRUE}
Actually, the total leaf primordia number is slightly less than the total cohort number.
```

### Leaf appearance 
A new leaf is appeared when the node number is increased by 1 at the main stem. Consequently, the appearance rate of leaf cohort is equal to phyllochron.


<div class="fig-output">

```{r leaf-appear-number, fig.cap='The node number in the main stem and appeared cohort number'}
y_cols <- c('Wheat.Structure.MainStemNodeNo',
            'Wheat.Leaf.AppearedCohortNo')

plot_report(df, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Number')

```
</div>

## Other periods

* Growth duration is defined as a phyllochron.
* Lag duration is defined as 4 phyllochrons for leaf appeared during vegetative period (from emergence to terminal spikelet). For leaf cohort apeared during stem alongtation period (from terminal spikelet to flag leaf), the lag duration equals to total length from stage `FlagLeaf` to stage `EndGrainFill` minus 3 phyllochron (`senescence duration`).

```{block, type='rmdnote'}
It could be only for flag leaf for extra longer lag duration.

```

* Senescence duration is defined as 3 phyllochrons.
* Detachment lag and dutachment duration are set as a big value `1000000` which assumes no detachment in wheat.


<div class="fig-output">
```{r leaf-cohort-number, fig.asp = 1.4, fig.cap='Initialized, appeared and expanding cohort number'}
y_cols <- c(
            'Wheat.Leaf.ExpandingCohortNo',
            'Wheat.Leaf.InitialisedCohortNo',
            'Wheat.Leaf.AppearedCohortNo',
            'Wheat.Leaf.SenescingCohortNo',
            'Wheat.Leaf.DeadCohortNo')

plot_report(df, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Cohort number')


```
</div>




<div class="fig-output">
```{r leaf-number, fig.asp = 1.3, fig.cap='Appeared number of green, senesced and total leaves'}
y_cols <- c(
    'Wheat.Leaf.PlantAppearedLeafNo',
    'Wheat.Leaf.PlantAppearedGreenLeafNo',
    'Wheat.Leaf.PlantsenescedLeafNo')

plot_report(df, x_var, y_cols, x_lab = x_lab, 
            y_lab = 'Leaf number')


```
</div>



## Leaf area index and coverage

<div class="fig-output">
```{r leaf-lai, fig.cap='Leaf area index', fig.subcap=c('Stage', 'Thermal time')}
y_cols <- c(
    'Wheat.Leaf.LAI', 
'Wheat.Leaf.LAIDead',
'Wheat.Leaf.LAITotal')
plot_report(df, x_var, y_cols, x_lab = x_lab, y_lab = 'Leaf area index')

```
</div>


<div class="fig-output">
```{r leaf-cover, fig.cap='Coverage', fig.subcap=c('Stage', 'Thermal time')}
y_cols <- c(
    'Wheat.Leaf.CoverGreen',
    'Wheat.Leaf.CoverDead',
    'Wheat.Leaf.CoverTotal')
plot_report(df, x_var, y_cols, x_lab = x_lab, y_lab = 'Coverage')

```
</div>





