# Structure {#cha-structure}


```{r read_data}
library(readr)
library(dplyr)
library(tidyr)
source('utility.R')
report <- read_csv('process_test/simulation.db.Report.csv')

df <- report %>% 
    filter(grepl('15TraitMod', Name),
           Management == 'IHN',
           Cultivar == 'hartog')

```


The Structure model predicts the development and mortality of phytomer and branch (tiller) according to plastochron and phyllochron. 




## Promordia and node number

Three primordias are initizliaed at stage Emergence (Section \@ref(stage-period)). The primordia number in main stem (MainStemPrimordiaNo, Section \@ref(output-structure)) is daily increased according to plastochron (Section \@ref(plastochron-phyllochron)) until stage Terminal Spikelet (Section \@ref(stage-period)). The leaf (`node` in [next generation APSIM](https://github.com/APSIMInitiative/ApsimX)) number in the main stem is daily increased according to the phyllochron (Section \@ref(plastochron-phyllochron)) until maximum leaf number is reached. 




The total leaf number in the main stem (MainStemFinalNodeNumber, Section \@ref(output-structure)) is initialized as 30 and reset as the primordia number at stage Terminal Spikelet (Section \@ref(stage-period)). The node number in the main stem (MainStemNodeNo, Section \@ref(output-structure)) is daily increasing since stage  Emergence (Section \@ref(stage-period)) until reach the final node number according to the `phyllochron` and daily thermal time. 



<div class="fig-output">
```{r final-node-number, fig.cap='Final node number in main stem'}


y_cols <- c(
    'Wheat.Structure.MainStemFinalNodeNumber')
x_var <- 'Wheat.Phenology.Stage'

plot_report(df, x_var, y_cols, x_lab = 'Stage', y_lab = 'Final node number in main stem')

```
</div>



Daily changes of primordia ($\Delta N_{pri}$) and node (leaf) ($\Delta N_{node}$) number in main stem are calculated using plastochron ($P_{pla}$) and phyllochron ($P_{phy}$), respectively, after plant stage Emergence (Section \@ref(stage-period) and Figure \@ref(fig:delta-node)).

$$
 \Delta N_{pri}=rac{\Delta TT_{d}}{P_{pla}}
$$

$$
 \Delta N_{node}=rac{\Delta TT_{t}}{P_{phy}}
$$

where, $\Delta TT_{t}$ is the daily thermal time, which calculates from parameter `ThermalTime`. $P_{pla}$ and $P_{phy}$ calculates from parameter `MainStemPrimordiaInitiationRate` (plastochron) and `MainStemNodeAppearanceRate` (phyllochron), respectively (Section \@ref(plastochron-phyllochron)).



<div class="alert alert-danger"><p>
The daily delta primodia number is not a output variable.
</p></div>



<div class="fig-output">
```{r delta-node, fig.cap='Daily increase of node number in main stem'}
y_cols <- c('Wheat.Structure.DeltaNodeNumber')
x_var <- 'Wheat.Phenology.Stage'

plot_report(df, x_var, y_cols, x_lab = 'Stage', y_lab = 'Daily increase of node number in main stem')
```
</div>


Total number of primordia ($N_{pri}$) and node ($N_{node}$) in main stem are summarised since initialisation.

$$
    N_{pri}=\sum_{t=T_{0}}^{T}\Delta N_{p}
$$

$$
    N_{node}=\sum_{t=T_{0}}^{T}\Delta N_{n}
$$

where, $T_{0}$ is day of plant initialisation which is set by Leaf model (Emergence for wheat).  $T$ is today. In the Structure model, the primordia and node numbers are not calculated for branches or tillers, but only for main stem (Figure \@ref(fig:node-number)). 



<div class="fig-output">
```{r node-number, fig.cap='Primordia and node number in main stem'}
y_cols <- c(
    'Wheat.Structure.MainStemNodeNo', 
    'Wheat.Structure.MainStemPrimordiaNo')
x_var <- 'Wheat.Phenology.Stage'

plot_report(df, x_var, y_cols, x_lab = 'Stage', y_lab = 'Primordia or node number in main stem')

```
</div>


## Tillering

<div class="alert alert-danger"><p>
The tiller number is too sensitive to WSC stress (x = [0.1, 0.2]; y = [0, 1]). This feature is disabled in all analysis
</p></div>



In [next generation APSIM](https://github.com/APSIMInitiative/ApsimX), tillering for wheat is referred as branching. New tillers are initialised when increase of the node number in 
main stem ($\Delta N_{node}$) is more than 1 although the branching rate ($\Delta N_{branch}$) is calculate everyday (Figure \@ref(fig:tiller-number)). 

The new branch number for each plant 
is specified by parameter BranchingRate ($\Delta N_{branch}$), which could be a function of 
branch number on leaf rank in main stem.
$$
     P_{branch} = P \times \sum_{t=T_{0}}^{T}\Delta N_{branch}
$$


The branching rate is defined by potential branching rate and stresses (nitrogen and WSC). From stage Emergence to Terminal Spikelet (Section \@ref(stage-period)), the potential branching rate is defined as  a function of number of appreared cohorts in the main stem (Figure \@ref(fig:branching-rate)). Beyond this period, the branching rate is set as zero. 


<div class="fig-input">
```{r branching-rate, fig.cap='Branching rate of APSIM-Wheat as a function of appreared cohort number'}
xpath <- '//Name[text()="PotentialBranchingRate"]'
plot_xypair(pmf, xpath, x_lab = 'Number of appeared cohorts', y_lab = 'Branching rate')

```
</div>


Two stresses are defined in the APSIM-Wheat inclduing nitrogen and WSC. A simple sensitivity analysis indicates the branching rate is too sensitive to WSC with default values (x = [0.1, 0.2]; y = [0, 1]). So, this feature is disabled for further analysis. 

The nitrogen stress is calculated as a function of fraction of nitrogen supply relative to nitrogen demand which is exported from the Arbitrator module (Chaptor \@ref(cha:arbitrator)). Wheat module assumes no nitrogen stress when the nitrogen supply is bigger than 1.5 times of nitrogen demand (Figure \@ref(fig:branching-rate-nstress)). Nitreogen stress linearly recreases when supply/demand ratio less then 1.5 (<font color="red">Reference required.</font>)


<div class="fig-input">
```{r branching-rate-nstress, fig.cap='Nitrogen stress on branching rate as a function of fraction of nitrogen supply relative to nitrogen demand'}
xpath <- '//Name[text()="Nitrogen"]'
plot_xypair(pmf, xpath, x_lab = 'Fraction of nitrogen supply relative to nitrogen demand', y_lab = 'Effect of nitrogen stress on branching rate')

```
</div>




Figure \@ref(fig:tiller-number) shows the branching rate and total branching number in the test simulation without nitrogen stress on branching rate during branching period (from Emergence to Terminal Spikelet, Figure \@ref(fig:nitrogen-fn)).

<div class="fig-output">
```{r tiller-number, fig.cap='The branching rate and branch number for wheat'}
y_cols <- c('Wheat.Structure.BranchNumber', 
            'Wheat.Structure.BranchingRate')
x_var <- 'Wheat.Phenology.Stage'

plot_report(df, x_var, y_cols, x_lab = 'Stage', y_lab = 'Branch number or branching rate')

```
</div>



<div class="fig-output">
```{r nitrogen-fn, fig.cap='The fraction of nitrogen supply relative to nitrogen demand'}
y_cols <- c('Wheat.Arbitrator.FN')
x_var <- 'Wheat.Phenology.Stage'

p <- plot_report(
    df %>% filter(Wheat.Phenology.Stage < 10),
            x_var, y_cols, x_lab = 'Stage', y_lab = 'Ratio of nitrogen supply and demand')
p + geom_hline(yintercept = 1.5)

```
</div>



<div class="alert alert-danger"><p>
It seems PMF uses the branching rate one day before to calculate the branch number.
</p></div>

## Mortality

<div class="fig-output">
```{r tiller-number-mo, fig.cap='The mortality of tillers'}
y_cols <- c(
    
    'Wheat.Structure.BranchMortality',
    
    'Wheat.Structure.ProportionBranchMortality', 
            'Wheat.Structure.ProportionPlantMortality')


x_var <- 'Wheat.Phenology.Stage'

plot_report(df, x_var, y_cols, x_lab = 'Stage', y_lab = 'Mortality of branching')

```

</div>

## Population

Plant population ($P$) is initialised at sowing from Sow event, and 
daily reduced by the plant mortality ($\Delta P$).
$$
    P=P_{0} - \sum_{t=T_{0}}^{T}(\Delta P)
$$
where, $P_{0}$ is the sown population, which initialised at sowing.

Population of main stem number ($P_{ms}$) is calculated  
according to plant population ($P$) and primary bud number ($N_{bud}$) 
with default value 1. The unit of $P_{ms}$ is per square meter.
$$
    P_{ms}=P \times N_{bud}
$$

Population of total stem ($P_{stem}$) is summed up 
population of main stem ($P_{ms}$) and branches (($P_{branch}$)).
$$
    P_{stem} = P_{ms} + P_{branch}
$$

Three factors are considered to reduce the population of total stem ($P_{stem}$), i.e.
1) Plant mortality ($\Delta P$), 2) Drought($\Delta N_{drought}$), 
3) Shade ($\Delta N_{shade}$). 

During a day, branches are first killed by plant mortality which 
reduces population through killing all stems in a plant.
$$
P_{branch} = P_{branch} - rac{(P_{branch} + P_{ms})}{P_{ms}} \times \Delta P
$$

Then environmental stresses (drought and shade) only cause mortality of 
the remaining branches.
$$
    P_{branch} = P_{branch} \times [1 - (\Delta N_{drought}+\Delta N_{shade})]
$$
The mortalities, caused by drought ($\Delta N_{drought}$)  
and shade ($\Delta N_{shade}$), are calculated by parameters 
DroughtInducedBranchMortality and ShadeInducedBranchMortality, respectively.








